Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
revised conclusions

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.  For the inductive back-end we apply a timeout of 8 hours
per benchmark, and 24 hours for the interval arithmetic back-end.

@@

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}) \textcolor{red}{Pascal: Why they did not meet the criteria?}. 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
back-end.

\begin{table}[H]
\centering
\begin{tabular}{c | l r r | r l}
Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
$G_4$ & a\_ST1\_IMPL1        			 &  16 &   4 & 2704\,s & \\
$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
\end{tabular}

@@

We conclude from these results that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks within reasonable time frames.  For the 1 remaining benchmark
our approach failed to synthesise a stable controller in the requested time limits.
This can be addressed by either increasing the fixed point word widths considered or
using floating point arithmetic instead. 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}

@@

In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
solution for a digital controller given a continuous (or discrete) plant specification.
In particular, we have exploited the automatic synthesis of correct-by-construction 
digital controllers along with a model of their physical environment.
We have also modeled a digital equivalent of the physical plant by evaluating the 
effects of the quantisers (A/D and D/A converters) as time discretisation elements 
with quantisation noise. Experimental results show that the inductive back-end of our
CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
Further studies include the extension of this CEGIS-based approach for different classes of systems
({\it e.g.}, state-space) and also consider performance requirements while synthesising 
the digital controller.

>>>>

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.

@@

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}) \textcolor{red}{Pascal: Why they did not meet the criteria?}. 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes \textcolor{red}{Pascal: Why is it slower?}.

\begin{table}[H]
\centering
\begin{tabular}{c | l r r | r l}
Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
$G_4$ & a\_PL1\_SCH2\_IMPL1        &  16 &   4 & 2704\,s & \\
$G_4$ & a\_PL1\_SCH2\_IMPL2        &  16 &   8 & 538\,s  & \\
$G_4$ & a\_PL1\_SCH2\_IMPL3        &  16 &  12 & 12\,s   & \\
$G_4$ & a\_PL1\_SCH3\_IMPL1        &  16 &   4 & 318\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL2        &  16 &   8 & 967\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL3        &  16 &  12 & 9798\,s & \\
$G_4$ & a\_PL1\_SCH4\_IMPL1        &  16 &   4 & 6304\,s & \\
\end{tabular}

@@

We conclude from these results that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks within reasonable time frames. \textcolor{red}{Why do we fail to synthesise 1 controller?} 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}

@@

In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
solution for a digital controller given a continuous (or discrete) plant specification.
In particular, we have exploited the automatic synthesis of correct-by-construction 
digital controllers along with a model of their physical environment.
We have also modeled a digital equivalent of the physical plant by evaluating the 
effects of the quantisers (A/D and D/A converters) as time discretisation elements 
with quantisation noise. Experimental results show that our
CEGIS-based approach is able to synthesise stable controllers in most benchmarks
within reasonable time frames.
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
Further studies include the extension of this CEGIS-based approach for different classes of systems
({\it e.g.}, state-space) and also consider performance requirements while synthesising 
the digital controller.
